\plaintitle

### 2016-08-11 drafts/labor/cases.tex
notes from meeting

The exploration of crowdsourcing's potential and limits has principally looked at
manipulating and extending along three dimensions:
\begin{inlinelist}
  \item \nameref{sec:decomposition},
  \item \nameref{sec:workAbstraction}, and
  \item \nameref{sec:flexibility}
\end{inlinelist}.
% We will further discuss the ways that various contributions drive along these dimensions.
As we'll discuss through these dimensions,
exploring the extents to which work can be
decomposed,
contextually abstracted, and
made more resilient to attrition,
we'll also point to corresponding piecework literature addressing these aspects;
finally, we'll discuss how these elements will serve
to constrain the upper and lower bounds of crowdsourcing as it relates
to the question of the furthest limits of crowdsourcing.

@@

%      _                                          _ _   _             
%   __| | ___  ___ ___  _ __ ___  _ __   ___  ___(_) |_(_) ___  _ __  
%  / _` |/ _ \/ __/ _ \| '_ ` _ \| '_ \ / _ \/ __| | __| |/ _ \| '_ \ 
% | (_| |  __/ (_| (_) | | | | | | |_) | (_) \__ \ | |_| | (_) | | | |
%  \__,_|\___|\___\___/|_| |_| |_| .__/ \___/|___/_|\__|_|\___/|_| |_|
%                                |_|                                  
% lol i can't believe this worked i'm going to do this with every section.

@@

Piecework Piecework Piecework Piecework Piecework Piecework Piecework

@@

>>>>

The exploration of crowdsourcing's potential and limits has principally looked at
manipulating and extending along three dimensions:
\begin{inlinelist}
  \item \nameref{sec:decomposition},
  \item \nameref{sec:workAbstraction}, and
  \item \nameref{sec:flexibility}
\end{inlinelist}.
% We will further discuss the ways that various contributions drive along these dimensions.
As we'll discuss these dimensions,
exploring the extents to which work can be
decomposed,
contextually abstracted, and
made more resilient to attrition of various forms,
we'll also point to corresponding piecework literature addressing these aspects.
Finally, we'll discuss how these elements will serve
to constrain the upper and lower bounds of crowdsourcing as it relates
to the question of the furthest limits of crowdsourcing.

@@

%      _                                          _ _   _             
%   __| | ___  ___ ___  _ __ ___  _ __   ___  ___(_) |_(_) ___  _ __  
%  / _` |/ _ \/ __/ _ \| '_ ` _ \| '_ \ / _ \/ __| | __| |/ _ \| '_ \ 
% | (_| |  __/ (_| (_) | | | | | | |_) | (_) \__ \ | |_| | (_) | | | |
%  \__,_|\___|\___\___/|_| |_| |_| .__/ \___/|___/_|\__|_|\___/|_| |_|
%                                |_|                                  
% lol i can't believe this worked i'm going to do this with every (sub)*section.

@@

Piecework has seen work along this dimension spanning decades;
\citeauthor{thompson1913time} investigate some of the ways that
construction can benefit from the principles of scientific management.
\citeauthor{thompson1913time}'s thesis asserts that
task work is predicated on the accurate scientific management of work,
including the ``miscellaneous tasks''.
\citeauthor{thompson1913time} argues
--- as early as \citeyear{thompson1913time} ---
that ``\dots one may be challenged to find any class of work
involving labor either indoors or out--of--doors
where tasks cannot be fixed by proper time--study''
\cite{thompson1913time}.

@@

\subsubsection{So how does this affect crowdwork?}
The work we've seen so far 
\begin{itemize}
  \item worst case: assembling iPhones (extant)
  \item average case: railroad workers and assembly lines
  \item high (complexity) case: 
\end{itemize}

% what can be decomposed? what can be evaluated?
% technology/turuing completeness gets us a win
% predefined expertise? you can find someone almost instantly;
% ease of doing this makes it qualitatively different due to Channel Factors (diverting a channel/river)
% huddler paper cites some decomposition stuff workflows are good/bad at things
% 3-way slack w/msb and mav
% academy of management 
% van der ven paper ~1972 limits of workflows cited in daniela's flash orgs paper

### 2016-08-11 drafts/labor/introduction.tex
notes from meeting

\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}

@@

% From a wide range of academic and industrial perspectives
% and increasingly identifying the many stakeholders in digitally mediated work,
The extant body of work has ostensibly sought to answer one underlying question:
What does the future hold for work and those that do it? % expand on ...?
Researchers have offered their input on this open question along three major threads of scholarship:
% the driving motivation behind much of the research in this space has led us to ask,
% at a high level, three important questions:
\begin{enumerate}
  \item What are the limits of crowdsourcing?
  Perhaps more tightly constrained,
  what can and cannot be done by crowd workers?
  % (what are the \textbf{complexity limits}) \note{(hospitals at high level?) -- team scaffolds} \note{why is there a high limit? is that different with crowds?}
    \cite[for example, see][]{foundry,suzukiAtelier,KimStoria,yuanAlmost,YuEncouragingOutside,embracingErrorKrishna,Nebeling:2016:WCW:2858036.2858169,Hahn:2016:KAB:2858036.2858364};
  \item What forms of work design, and worker management and arrangement, are viable?
  % \note{time in motion studies; job design; } or is this more about managers, coops, etc...
    \cite[for example, see][]{bernsteinSoylent,sensitiveTasks,LykourentzouPersonalityMatters,KucherbaevReLauncher,Law:2016:CKC:2858036.2858144,Cai:2016:CRI:2858036.2858237,Chang:2016:ACC:2858036.2858411,Newell:2016:OMA:2858036.2858490}; and%
  \item What will work and the place of work look like for the workers?
    \cite[for example, see][]{turkopticon,storiesIraniSilberman,dynamo,crowdcollab,whyWouldAnyoneBrewer,takingAHITMcInnis}
    % \note{these questions are all a little guilty of vagueness but this feels especially ``meh''}
\end{enumerate}

@@

@@

We offer a framing for crowd work spanning the aforementioned industries
collectively as a contemporary instantiation of ``piecework''.
Piecework as a metaphor for the type of work at hand is not new.
Indeed,
\citeauthor{crowdworkFuture}
in
\citeyear{crowdworkFuture}
referenced crowd work as ``piecework'' briefly
as a loose analogy to the form of work emerging at the time
% but not given as much weight as it perhaps could have been
\cite{crowdworkFuture}.
% ``Piecework'' here makes use of
% a term historically used to describe work done in the home,
% in manageable tasks,
% often involving clear instructions
% and payment only for work completed, not work done
% (the differentiation then being that
% one would be paid for the \textit{output} of the work,
% not the \textit{duration}).

@@

\onlyinsubfile{
  \balance{}
  \printbibliography
}

>>>>

\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother

% \usepackage[style=alphabetic]{biblatex}
\begin{document}

@@

% From a wide range of academic and industrial perspectives
% and increasingly identifying the many stakeholders in digitally mediated work,
The extant body of work has ostensibly sought to answer one underlying question:
What does the future hold for work and those that do it? % expand on ...?
Researchers have offered their input on this open question along three major threads of scholarship:
% the driving motivation behind much of the research in this space has led us to ask,
% at a high level, three important questions:
\begin{enumerate}
  \item What are the limits of crowdsourcing?
  Perhaps more tightly constrained,
  what can and cannot be done by crowd workers?
  % (what are the \textbf{complexity limits}) \note{(hospitals at high level?) -- team scaffolds} \note{why is there a high limit? is that different with crowds?}
    \cite{foundry,suzukiAtelier,KimStoria,yuanAlmost,YuEncouragingOutside,embracingErrorKrishna,Nebeling:2016:WCW:2858036.2858169,Hahn:2016:KAB:2858036.2858364};
  \item What forms of work design, and worker management and arrangement, are viable?
  % \note{time in motion studies; job design; } or is this more about managers, coops, etc...
    \cite{bernsteinSoylent,sensitiveTasks,LykourentzouPersonalityMatters,KucherbaevReLauncher,Law:2016:CKC:2858036.2858144,Cai:2016:CRI:2858036.2858237,Chang:2016:ACC:2858036.2858411,Newell:2016:OMA:2858036.2858490}; and%
  \item What will work and the place of work look like for the workers?
    \cite{turkopticon,storiesIraniSilberman,dynamo,crowdcollab,whyWouldAnyoneBrewer,takingAHITMcInnis}
    % \note{these questions are all a little guilty of vagueness but this feels especially ``meh''}
\end{enumerate}

@@

% so CW?
% mechanism/limitation in pw?
% differences in cw? tech/access to intelligence?
% predicted outcome then? -> decompose effort/expertise access
% possible quirks/diffs?

@@

We offer a framing for crowd work spanning the aforementioned industries
collectively as a contemporary instantiation of ``piecework''.
Piecework as a metaphor for the type of work at hand is not new.
Indeed,
\citeauthor{crowdworkFuture}
in
\citeauthor{crowdworkFuture}
referenced crowd work as ``piecework'' briefly
as a loose analogy to the form of work emerging at the time
% but not given as much weight as it perhaps could have been
\cite{crowdworkFuture}.
% ``Piecework'' here makes use of
% a term historically used to describe work done in the home,
% in manageable tasks,
% often involving clear instructions
% and payment only for work completed, not work done
% (the differentiation then being that
% one would be paid for the \textit{output} of the work,
% not the \textit{duration}).

@@

\onlyinsubfile{
  \balance{}
  % \bibliography{references}
  \printbibliography
}
